Does the leaf economic spectrum hold within plant functional types? A Bayesian hierarchical meta-analysis

### 2018-02-16 manuscript/index.Rmd
Revise author list

---
title: "Does the leaf economic spectrum hold within plant functional types? A Bayesian hierarchical meta-analysis"
author:
  - >
    Alexey N. Shiklomanov$^1$
    Elizabeth M. Cowdery$^1$,
    Michael Bahn$^2$,
    Chaeho Byun$^3$,
    Joseph Craine$^4$,
    Andrés Gonzalez-Melo$^5$,
    Alvaro G. Gutiérrez$^6$,
    Steven Jansen$^7$,
    Nathan Kraft$^8$,
    Koen Kramer$^{9}$,
    Vanessa Minden$^{10,11}$,
    Ülo Niinemets$^{12}$,
    Yusuke Onoda$^{13}$,
    Enio Egon Sosinski$^{14}$,
    Nadejda A. Soudzilovskaia$^{15}$,
    Michael C. Dietze$^1$
bibliography:
  - library.bib
  - extra.bib
  - tryrefs.bib
csl: new-phytologist.csl
output:
  bookdown::word_document2:
    toc: no
    reference_docx: ~/Projects/misc/pandoc-docx-template/custom.docx
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    includes:
      in_header: preamble.tex
---
<div custom-style="Affiliation">
$^1$Department of Earth & Environment, Boston University, Boston, MA 02215, USA;
$^2$Institute of Ecology, University of Innsbruck, 6020 Innsbruck, Austria;
$^3$School of Biological Sciences, Seoul National University, Gwanak-ro 1, 08826, Seoul, Seoul, South Korea;
$^4$Jonah Ventures, Manhattan, KS 66502, USA;
$^5$Universidad del Rosario. Facultad de Ciencias Naturales y Matemáticas. Carrera 26 #63B-48. Bogotá, Colombia;
$^6$Departamento de Ciencias Ambientales y Recursos Naturales, Facultad de Ciencias Agronomicas, Universidad de Chile, Av. Santa Rosa 11315, La Pintana 8820808, Santiago, Chile;
$^7$Institute of Systematic Botany and Ecology, Ulm University, Ulm, Germany;
$^8$Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA 90095, USA;
$^{9}$Vegetation, Forest, and Landscape Ecology, Wageningen Environmental Research and Wageningen University, Wageningen, Gelderland, The Netherlands;
$^{10}$Institute for Biology and Environmental Sciences, Carl von Ossietzky-University of Oldenburg, Carl von Ossietzky Str. 9-11, 26129 Oldenburg, Germany;
$^{11}$Department of Biology, Ecology and Evolution, Vrije Universiteit Brussel, Pleinlaan 2, 1050 Brussels;
$^{12}$Institute of Agricultural and Environmental Sciences, Estonian University of Life Sciences, Kreutzwaldi 1, 51014 Tartu, Estonia;
$^{13}$Graduate School of Agriculture, Kyoto University, Kyoto, 606-8502, Japan;
$^{14}$Embrapa Temperate Agriculture, Rodovia BR 392, Km 78, CEP 96010-971 Pelotas, RS, Brazil;
$^{15}$Conservation Biology Department, Institute of Environmental Sciences, Leiden University, Leiden, The Netherlands
</div>

>>>>

---
title: "Does the leaf economic spectrum hold within plant functional types? A Bayesian hierarchical meta-analysis"
author:
  - >
    Alexey N. Shiklomanov$^1$
    Elizabeth M. Cowdery$^1$,
    Michael Bahn$^2$,
    Chaeho Byun$^3$,
    Joseph Craine$^4$,
    Andrés Gonzalez-Melo$^5$,
    Steven Jansen$^6$,
    Nathan Kraft$^7$,
    Koen Kramer$^{8}$,
    Vanessa Minden$^{9,10}$,
    Ülo Niinemets$^{11}$,
    Yusuke Onoda$^{12}$,
    Enio Egon Sosinski$^{13}$,
    Nadejda A. Soudzilovskaia$^{14}$,
    Michael C. Dietze$^1$
bibliography:
  - library.bib
  - extra.bib
  - tryrefs.bib
csl: new-phytologist.csl
output:
  bookdown::word_document2:
    toc: no
    reference_docx: ~/Projects/misc/pandoc-docx-template/custom.docx
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    includes:
      in_header: preamble.tex
---
<div custom-style="Affiliation">
$^1$Department of Earth & Environment, Boston University, Boston, MA 02215, USA;
$^2$Institute of Ecology, University of Innsbruck, 6020 Innsbruck, Austria;
$^3$School of Biological Sciences, Seoul National University, Gwanak-ro 1, 08826, Seoul, Seoul, South Korea;
$^4$Jonah Ventures, Manhattan, KS 66502, USA;
$^5$Universidad del Rosario. Facultad de Ciencias Naturales y Matemáticas. Carrera 26 #63B-48. Bogotá, Colombia;
$^6$Institute of Systematic Botany and Ecology, Ulm University, Ulm, Germany;
$^7$Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA 90095, USA;
$^{8}$Vegetation, Forest, and Landscape Ecology, Wageningen Environmental Research and Wageningen University, Wageningen, Gelderland, The Netherlands;
$^{9}$Institute for Biology and Environmental Sciences, Carl von Ossietzky-University of Oldenburg, Carl von Ossietzky Str. 9-11, 26129 Oldenburg, Germany;
$^{10}$Department of Biology, Ecology and Evolution, Vrije Universiteit Brussel, Pleinlaan 2, 1050 Brussels;
$^{11}$Institute of Agricultural and Environmental Sciences, Estonian University of Life Sciences, Kreutzwaldi 1, 51014 Tartu, Estonia;
$^{12}$Graduate School of Agriculture, Kyoto University, Kyoto, 606-8502, Japan;
$^{13}$Embrapa Temperate Agriculture, Rodovia BR 392, Km 78, CEP 96010-971 Pelotas, RS, Brazil;
$^{14}$Conservation Biology Department, Institute of Environmental Sciences, Leiden University, Leiden, The Netherlands
</div>
